Dependent Object Types

### 2012-08-05 article.tex
revised dot-sub

    \end{multicols}
}

@@

>>>>

    \end{multicols}
} % END dot-sub

\subsection*{Subtyping}

\figref{dot-sub} defines the subtyping judgement $\Gamma \ts S
\sub T$ which states that in environment $\Gamma$ type $S$ is a
subtype of type $T$. Subtyping is regular with respect to $\wfe$: if
type $S$ is a subtype of type $T$, then $S$ and $T$ are well-formed
and expanding. Though this regularity limits our calculus to
$\wfe$-types, this limitation allows us to show that subtyping is
transitive, as discussed in section~\ref{dot-preservation}.

@@

\section{Counterexamples to Preservation}\label{dot-preservation}

\section{Type Safety via Logical Relations}\label{dot-type-safety}

\section{Conclusion}\label{conclusion}
